\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-14 doc/sw-system.tex
Changed 'Stage II' to 'Stage 2', for consistency with figures but also to reserve roman numerals for papers. #207

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both Stages I and II of the \cfhtls project, with the
total numbers of agents and subjects for comparison.   These numbers allow us
to quantify the efficiency of the system.

>>>>

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both \StageOne and \StageTwo of the \cfhtls project, with the
total numbers of agents and subjects for comparison.   These numbers allow us
to quantify the efficiency of the system.
